Advances in Artificial Intelligence for Data Visualization: Developing Computer Vision Models to Automate Reading of Data Plots, with Application to Predictive Model Diagnostics

### 2022-03-09 Milestone_1/01-chap1.Rmd
add design of the automatic system

Depended on the inputs and outputs of the automatic system, various designs arised.

A system can be summarised

@@

The term content-based image retrieval (CBIR) was first introduced by @kato_database_1992 as a field of study which aimes to retrieve image from large-scale image databases based on information derived from the image itself, such as colour, shape and texture [@rafiee_review_2010]. According to @zhou_recent_2017, reverse image search is one of the CBIR query technique and is sometimes called query by example (QBE), which performs image search based on the image example provide by the user. Since QBE is the most intuitive query formation, it has been widely explored in the research on CBIR and search engines such as Google Image [@google_google_2022] and TinEye [@tineye_tineye_2022] provide accessible search by image services to public. In CBIR, the most common method for comparing images is using image similarity or image distance metrics, which takes into account various features extracted from the image [@zhou_recent_2017].

>>>>

Depending on the desired input(s) and output(s) of the automatic system, the system can be designed in various ways. We considered the most general design would be which took inputs of multiple image files corresponding to data plots of a lineup, and outputted a list of selections made by the system. This was identical to what was provided to and asked of the observer in the human subject experiment.

Decision also needed to be made for the input and output format of the computer vision models. If the model took multiple data plots of a lineup as inputs, and outputted the predicted probabilities of the data plot being the most different one, then the post-processing step of the system would be a mapping from a list of numeric values between zero and one to a list of one-hot encoded binary values denoting the selections. This mapping could be an indicator function, i.e. a threshold for deciding whether to select a data plot or not. It could also be a combination of the indicator function and the order statistic to select the $M$ most likely data plots, where $M$ was a user-defined positive integer. In fact, the choice of the mapping function was flexible.

This design was reasonable but we found that it was difficult and slow to train the model. Instead, a simpler model design was used. The model took only one data plot as input at a time, and predicted the probability of the data plot being a null plot. In this case, the post-processing step was an indicator function for deciding whether the data plot is a null plot. By evaluating all $m$ plots of a lineup, multiple selections can be made.

### Model Architecture and Model Training

As mentioned in Section \ref{se:limitation}, modern computer vision model is built upon the deep neural network

@@

The term content-based image retrieval (CBIR) was first introduced by @kato_database_1992 as a field of study which aims to retrieve image from large-scale image databases based on information derived from the image itself, such as colour, shape and texture [@rafiee_review_2010]. According to @zhou_recent_2017, reverse image search is one of the CBIR query technique and is sometimes called query by example (QBE), which performs image search based on the image example provide by the user. Since QBE is the most intuitive query formation, it has been widely explored in the research on CBIR and search engines such as Google Image [@google_google_2022] and TinEye [@tineye_tineye_2022] provide accessible search by image services to public. In CBIR, the most common method for comparing images is using image similarity or image distance metrics, which takes into account various features extracted from the image [@zhou_recent_2017].

### 2022-03-09 Milestone_1/_book/thesis.tex
add design of the automatic system

Depended on the inputs and outputs of the automatic system, various designs arised.

A system can be summarised

@@

The term content-based image retrieval (CBIR) was first introduced by \textcite{kato_database_1992} as a field of study which aimes to retrieve image from large-scale image databases based on information derived from the image itself, such as colour, shape and texture \autocite{rafiee_review_2010}. According to \textcite{zhou_recent_2017}, reverse image search is one of the CBIR query technique and is sometimes called query by example (QBE), which performs image search based on the image example provide by the user. Since QBE is the most intuitive query formation, it has been widely explored in the research on CBIR and search engines such as Google Image \autocite{google_google_2022} and TinEye \autocite{tineye_tineye_2022} provide accessible search by image services to public. In CBIR, the most common method for comparing images is using image similarity or image distance metrics, which takes into account various features extracted from the image \autocite{zhou_recent_2017}.

>>>>

Depending on the desired input(s) and output(s) of the automatic system, the system can be designed in various ways. We considered the most general design would be which took inputs of multiple image files corresponding to data plots of a lineup, and outputted a list of selections made by the system. This was identical to what was provided to and asked of the observer in the human subject experiment.

Decision also needed to be made for the input and output format of the computer vision models. If the model took multiple data plots of a lineup as inputs, and outputted the predicted probabilities of the data plot being the most different one, then the post-processing step of the system would be a mapping from a list of numeric values between zero and one to a list of one-hot encoded binary values denoting the selections. This mapping could be an indicator function, i.e.~a threshold for deciding whether to select a data plot or not. It could also be a combination of the indicator function and the order statistic to select the \(M\) most likely data plots, where \(M\) was a user-defined positive integer. In fact, the choice of the mapping function was flexible.

This design was reasonable but we found that it was difficult and slow to train the model. Instead, a simpler model design was used. The model took only one data plot as input at a time, and predicted the probability of the data plot being a null plot. In this case, the post-processing step was an indicator function for deciding whether the data plot is a null plot. By evaluating all \(m\) plots of a lineup, multiple selections can be made.

\hypertarget{model-architecture-and-model-training}{%
\subsection{Model Architecture and Model Training}\label{model-architecture-and-model-training}}

As mentioned in Section \ref{se:limitation}, modern computer vision model is built upon the deep neural network

@@

The term content-based image retrieval (CBIR) was first introduced by \textcite{kato_database_1992} as a field of study which aims to retrieve image from large-scale image databases based on information derived from the image itself, such as colour, shape and texture \autocite{rafiee_review_2010}. According to \textcite{zhou_recent_2017}, reverse image search is one of the CBIR query technique and is sometimes called query by example (QBE), which performs image search based on the image example provide by the user. Since QBE is the most intuitive query formation, it has been widely explored in the research on CBIR and search engines such as Google Image \autocite{google_google_2022} and TinEye \autocite{tineye_tineye_2022} provide accessible search by image services to public. In CBIR, the most common method for comparing images is using image similarity or image distance metrics, which takes into account various features extracted from the image \autocite{zhou_recent_2017}.
